Scalar on Function Regression

### 2021-12-31 Presentation/slides.tex
Slides update

% Title page details: 
\title{{\color{red} TEMPORARY TITLE}}
\author{Jona Willnow, Jakob Juergens, Jonghun Baek}
\date{{\color{red}}Presentation Day}

@@

	% I'm not really a fan of a table of contents in short presenations (Jakob)
	% Outline frame
	%\begin{frame}{Outline}
	%	\tableofcontents
	%\end{frame}

	\begin{frame}{Lorem Ipsum}
		Lorem Ipsum dolor sit amet.
	\end{frame}

>>>>

% Title page details: 
\title{Scalar on Function Regression}
\author{Jonathan Willnow, Jakob Juergens, Jonghun Baek}
\date{{\color{red}}Presentation Day}

@@

	% I'm not really a fan of a table of contents in short presentations (Jakob)
	% Outline frame
	%\begin{frame}{Outline}
	%	\tableofcontents
	%\end{frame}

	\begin{frame}{Introduction}
		Jona \\
		Introductory Example $\rightarrow$ Octane/NIR-spectrum
	\end{frame}

	\begin{frame}{Theory}
		Jona \\
		Motivation from multivariate regression (multivariate dgp).
	\end{frame}

	\begin{frame}{Theory}
		Jonghun
		\begin{itemize}
			\item Random Functions (name square integrable functions)
			\item Motivate continuous stochastic processes (growth curves/electricity consumption/yield curves/stonks)
			\item Use curves to predict a scalar response (show typical dgp)
		\end{itemize}
	\end{frame}

	\begin{frame}{Theory}
		Jonghun
		\begin{itemize}
			\item Basis expansions (b-splines and fourier)
			\item Talk about purposes
			\item Plots and show bias variance tradeoff
		\end{itemize}
	\end{frame}

	\begin{frame}{Theory}
		Jakob
		\begin{itemize}
			\item Random function represented as linear combination of basis functions
			\item Just transform to multiple linear regression setting
			\item You already know that from the beginning
		\end{itemize}
	\end{frame}

	\begin{frame}{Theory - FPCA}
		Jakob
		\begin{itemize}
			\item Let's assume you know the theory of PCA (pc from varcov matrix)
			\item Introduce mean and covariance functions of random functions
			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion)
			\item Sample Analog! (create a basis from observations and use for basis regression)
			\item Plot fpcs and approximation of function realization
		\end{itemize}
	\end{frame}

	\begin{frame}{Simulation Setup \& Application}
		Jona
		\begin{itemize}
			\item Compare b-spline / fourier regression chosen via criterion (cv/aic/...)
			\item Similar for fpca
			\item generate new curves from observed curves motivated by Karhunen-Loeve expansion
			\item Compare optimal variants with test and training sets
			\item Connect to Application
		\end{itemize}
	\end{frame}

	\begin{frame}{Summary}
		Jona \\
		Just summarize what we have done...
	\end{frame}

	\begin{frame}{further reading}
		Put footnotes here!
	\end{frame}
